\bf Hierarchical Forecasts Reconciliation

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Intution about MinT provided

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  It is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	First, the linear subspace onto which all points are projected, or the image of the projection, must be defined. In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.  Second, the direction along which points are projected must be defined.  This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection. A schematic of this is presented \todo{include}.   A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$. It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.

	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$. In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$. We will be discussing these projections distinctly in the next subsection\todo{needs work}.

	In MinT reconciliation, $\bm{R}'_\perp$ is taking the form $\bm{S}'{\bm{W}}^{-1}$, where it can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$. That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection. Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig:pointfr_sch}. In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space. Latter is also referred to as the Mahalonobis distance. We also note that the WLS is a special case of MinT where $\bm{W}^{-1}$ is a diagonal matrix.

	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
	We can provide a more general geometrical explanation to this optimality using the schematic in Figure \ref{fig:MinT_justification}. Consider the h-step ahead reconciled forecast errors. These can be always approximated by the insample h-step ahead forecast errors. Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$. Therefore if you project $\hat{\bm{y}}$ along the direction of these in-sample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic. Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/MinT_justification}
		}
		\caption{A schematic to represent MinT reconciliation. Points in orange colour represent the insample errors. $\bm{R}$ shows the direction of the insample errors. $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification}
	\end{figure}

>>>>

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  It is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.  
    f
    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	\subsection{MinT}

	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{Wickramasuriya2017} has an additional optimality property.  \cite{Wickramasuriya2017} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.  This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.  Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts.  One such forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.  Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/insampledir}
		}
		\caption{A schematic to represent MinT reconciliation. Points in orange colour represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace. $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
	\end{figure}

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/oblique_justification2}
		}
		\caption{A schematic to represent MinT reconciliation. Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
	\end{figure}
